Binocular integration of chromatic and luminance signals

### 2024-03-31 manuscript.Rmd
Fixed to download MCS fits if missing

if (processdata < 2){
 if (!file.exists('local/simplexfits.RData')){osf_download(osffiles[which(osffiles$name=='simplexfits.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/stanfit1.RData')){osf_download(osffiles[which(osffiles$name=='stanfit1.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/stanfit2.RData')){osf_download(osffiles[which(osffiles$name=='stanfit2.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/stanfit3.RData')){osf_download(osffiles[which(osffiles$name=='stanfit3.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/stanfit4.RData')){osf_download(osffiles[which(osffiles$name=='stanfit4.RData'),],'local/',progress=TRUE)}
}

>>>>

if (processdata < 2){
 if (!file.exists('local/simplexfits.RData')){osf_download(osffiles[which(osffiles$name=='simplexfits.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/stanfit1.RData')){osf_download(osffiles[which(osffiles$name=='stanfit1.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/stanfit2.RData')){osf_download(osffiles[which(osffiles$name=='stanfit2.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/stanfit3.RData')){osf_download(osffiles[which(osffiles$name=='stanfit3.RData'),],'local/',progress=TRUE)}
 if (!file.exists('local/stanfit4.RData')){osf_download(osffiles[which(osffiles$name=='stanfit4.RData'),],'local/',progress=TRUE)}
if (!file.exists('local/MCSfit.RData')){osf_download(osffiles[which(osffiles$name=='MCSfit.RData'),],'local/',progress=TRUE)}
}
